Supplementary materials for 'Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-23 analysis/paper/supplementary_materials.Rmd
Update supplementary figures

```{r, setup, echo=FALSE, message=FALSE, include=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggpubr",
  "grDevices",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "patchwork",
  "posterior",
  "report",
  "rope",
  "rsvg",
  "tidyr",
  "tools"
)

@@

@@

```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability. Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
y_labs <- gsub("abbreviation", "", parameters(m_f1)$Parameter)
y_labs <- rev(gsub("b_", "", y_labs))
y_labs <- y_labs[c(21:22, 1:20)]

p <- plot(equivalence_test(m_f1)) +
  scale_y_discrete(labels = y_labs)

@@

```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability. Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
y_labs <- rev(gsub("b_", "", y_labs))
y_labs <- y_labs[c(21:23, 1:20)]

p <- plot(equivalence_test(m_f2)) +
  scale_y_discrete(labels = y_labs)

@@

```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability. Scoring for 'Code Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
p <- plot(equivalence_test(m_g1))

@@

```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability. Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
p <- plot(equivalence_test(m_g2))

@@

```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability. Scoring for 'Code Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
p <- plot(equivalence_test(m_h1))

@@

```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability.  Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
p <- plot(equivalence_test(m_h2))

>>>>

```{r, setup, echo=FALSE, message=FALSE, include=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "english",
  "effectsize",
  "extrafont",
  "flextable",
  "ggpubr",
  "grDevices",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "patchwork",
  "posterior",
  "report",
  "rope",
  "rsvg",
  "tidyr",
  "tools"
)

@@

options(mc.cores = parallel::detectCores())

@@

```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Effect sizes for a model testing the effect of the publishing journal on articles\' supporting code availability. Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
m_f1_es <- effectsize(m_f1)

m_f1_es <-
  filter(m_f1_es,
         Parameter != "b_Intercept[1]" &
           Parameter != "b_Intercept[2]")

ylabs <- gsub("b_abbreviation", "", m_f1_es$Parameter)

p <- plot(m_f1_es) +
   scale_y_discrete(labels = rev(ylabs))

@@

```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability. Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
m_f2_es <- effectsize(m_f2)

m_f2_es <-
  filter(
    m_f2_es,
    Parameter != "b_Intercept[1]" &
      Parameter != "b_Intercept[2]" &
      Parameter != "b_Intercept[3]"
  )

ylabs <- gsub("b_abbreviation", "", m_f2_es$Parameter)

p <- plot(m_f2_es) +
   scale_y_discrete(labels = rev(ylabs))

@@

```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability. Scoring for 'Code Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
m_g1_es <- effectsize(m_g1)

m_g1_es <-
  filter(m_g1_es,
         Parameter != "b_Intercept[1]" &
           Parameter != "b_Intercept[2]")

ylabs <- gsub("b_abbreviation", "", m_g1_es$Parameter)

p <- plot(m_g1_es) +
   scale_y_discrete(labels = rev(ylabs))

@@

```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability. Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
m_g2_es <- effectsize(m_g2)

m_g2_es <-
  filter(
    m_g2_es,
    Parameter != "b_Intercept[1]" &
      Parameter != "b_Intercept[2]" &
      Parameter != "b_Intercept[3]"
  )

ylabs <- gsub("b_abbreviation", "", m_g2_es$Parameter)

p <- plot(m_g2_es) +
   scale_y_discrete(labels = rev(ylabs))

@@

```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability. Scoring for 'Code Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
m_h1_es <- effectsize(m_h1)

m_h1_es <-
  filter(m_h1_es,
         Parameter != "b_Intercept[1]" &
           Parameter != "b_Intercept[2]")

ylabs <- gsub("b_abbreviation", "", m_h1_es$Parameter)

p <- plot(m_h1_es) +
   scale_y_discrete(labels = rev(ylabs))

@@

```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability.  Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
m_h2_es <- effectsize(m_h2)

m_h2_es <-
  filter(
    m_h2_es,
    Parameter != "b_Intercept[1]" &
      Parameter != "b_Intercept[2]" &
      Parameter != "b_Intercept[3]"
  )

ylabs <- gsub("b_abbreviation", "", m_h2_es$Parameter)

p <- plot(m_h2_es) +
   scale_y_discrete(labels = rev(ylabs))
